---
WiNS Collabathon 2023
Network Scince Institute at Northeastern University
Rafiazka Hilman

===============================================================================================================
===============================================================================================================
---

# Packages
We will be using these packages (remove the # in front, to install):
```{r message=FALSE}
#install.packages("igraph")
#install.packages("tidytext")
#install.packages("tm")
#install.packages("ggplot2")
#install.packages("dplyr")
#install.packages("stringr")
#install.packages("tidyr")
#install.packages("purrr")
#install.packages("arrow")
#install.packages("ape")
#install.packages("pluralize")
#install.packages("networkD3)

library(igraph)
library(tidytext) #text management
library(tm) #text mining 
library(ggplot2) #graphical plot
library(dplyr) #data management
library(stringr)
library(tidyr)
library(purrr)
library(arrow)
library(ape)
library(pluralize)
library(networkD3)
```


We'll use curated ArXiv dataset from Kaggle. 
It contains above mentioned abstracts containing 'climate_change'.
https://www.kaggle.com/datasets/Cornell-University/arxiv?datasetId=612177
```{r}
arxiv_climate_change <- read_parquet("arxiv_climate_change.parquet")
arxiv_climate_change$year<- substr(arxiv_climate_change$update_date, 1, 4)
arxiv_climate_change <- arxiv_climate_change %>% 
  filter(year %in% c("2007", "2008", "2009", "2010", "2011", "2012")) 
```



#2. Data Management and Cleaning Procedures
Step 1: Remove graphical parameter
```{r}
arxiv_climate_change$abstract <- str_replace_all(arxiv_climate_change$abstract,"[^[:graph:]]", " ")
```

Step 2: Create function to clean text
```{r}
#function
clean.text = function(x)
{
  # convert to lower case
  x = tolower(x)
  # remove punctuation
  x = gsub("[[:punct:]]", "", x)
  # remove numbers
  x = gsub("[[:digit:]]", "", x)
  # remove tabs
  x = gsub("[ |\t]{2,}", "", x)
  # remove blank spaces at the beginning
  x = gsub("^ ", "", x)
  # remove blank spaces at the end
  x = gsub(" $", "", x)
  # some other cleaning text
  x = gsub('[^[:graph:]]', ' ',x)
  x = gsub('[[:punct:]]', '', x)
  x = gsub('[[:cntrl:]]', '', x)
  x = gsub('\\d+', '', x)
  x = str_replace_all(x,"[^[:graph:]]", " ")
  return(x)
}
```

Step 3: Clean Text 
We only consider the abstract text. 
```{r}
arxiv_climate_change_clean <- clean.text(arxiv_climate_change$abstract) #run function
arxiv_climate_change_na <- which(arxiv_climate_change_clean == " ") #remove space
arxiv_climate_change_clean <- arxiv_climate_change_clean[arxiv_climate_change_clean != " "] #remove space
```



##3.4. Bigram Network 
Create dataframe containing stopwords in Dutch from 'tm' package.
```{r}
stopwords_df <- as.data.frame(stopwords(kind = "english"))
colnames(stopwords_df) <- "word"

remove_add <- c("can")
```


Bigram is a co-existence pairwise of words in the text.
Network 1: arxiv_climate_change
```{r}
#identify bigram
arxiv_climate_change_clean_df <- as.data.frame(arxiv_climate_change_clean)
colnames(arxiv_climate_change_clean_df) <- "text"

arxiv_climate_change_bigram <- arxiv_climate_change_clean_df %>% 
  unnest_tokens(
    input = text, 
    output = bigram, 
    token = 'ngrams', 
    n = 2
  ) %>% 
  filter(! is.na(bigram))

#filter stopword
arxiv_climate_change_bigram <- arxiv_climate_change_bigram %>% 
  tidyr::separate(col = bigram, into = c('word1', 'word2'), sep = ' ') %>%
  filter(! word1 %in% stopwords_df$word) %>% 
  filter(! word2 %in% stopwords_df$word) %>% 
  filter(! word1 %in% remove_add) %>% 
  filter(! word2 %in% remove_add) %>% 
  filter(! is.na(word1)) %>% 
  filter(! is.na(word2)) 

#singularization
arxiv_climate_change_bigram$word1 <- pluralize::singularize(arxiv_climate_change_bigram$word1) 
arxiv_climate_change_bigram$word2 <- pluralize::singularize(arxiv_climate_change_bigram$word2) 

#count frequency of bigram
arxiv_climate_change_bigram_count <- arxiv_climate_change_bigram %>% 
  count(word1, word2, sort = TRUE) %>% 
  rename(weight = n)
```


Construct original network
```{r}
arxiv_climate_change_network <-  arxiv_climate_change_bigram_count %>%
  graph_from_data_frame(directed = TRUE) #directed network

arxiv_climate_change_network <- as.undirected(
  arxiv_climate_change_network,
  mode = c("collapse"),
  edge.attr.comb = igraph_opt("edge.attr.comb") #trasnform as undirected and collpsing edges weight
)

climate_change_adj <- as_adjacency_matrix(
  arxiv_climate_change_network,
  type = c("both"),
  attr = NULL,
  edges = FALSE,
  names = TRUE,
  sparse = igraph_opt("sparsematrices")
)

length(V(arxiv_climate_change_network))
length(E(arxiv_climate_change_network))
fc_climate_change <- cluster_fast_greedy(arxiv_climate_change_network, weights = E(arxiv_climate_change_network)$weight)
fc_climate_change
```


Plot network: all
```{r, fig.height = 3, fig.width = 4, fig.align = "center"}
#node degree based on its total degree
V(arxiv_climate_change_network)$degree <- strength(graph = arxiv_climate_change_network, mode="all")

#png("net_climate_change_sub.png", width=600, height=350, res=300)
pdf(file = "climate_change_0712_net.pdf"   # The directory you want to save the file in
    ) # The height of the plot in inches
par(bg = 'black') # set background to black
plot(arxiv_climate_change_network, 
  vertex.color = 'lavender',
  #vertex.size = 0,
  vertex.size = V(arxiv_climate_change_network)$degree/500,
  vertex.label.color = membership(fc_climate_change), 
  #vertex.label.cex = log(V(arxiv_climate_change_network_sub)$degree)/100, #vertex label size
  vertex.label.cex = V(arxiv_climate_change_network)$degree/500, #vertex label size
  vertex.label.dist = 1.6,
  edge.color = 'white', 
  edge.width = E(arxiv_climate_change_network)$weight/30,   
  main = 'Bigram Network: Climate Change', 
  alpha = 100, edge.curved=0.4
)

dev.off()
```


Impose edge weight cutoff
```{r}
#subset by edge weight cutoff
climate_change_new <- subset(arxiv_climate_change_bigram_count, weight >= 5,
select=c(word1, word2, weight))

arxiv_climate_change_network <-  climate_change_new %>%
  graph_from_data_frame(directed = TRUE) #directed network

arxiv_climate_change_network <- as.undirected(
  arxiv_climate_change_network,
  mode = c("collapse"),
  edge.attr.comb = igraph_opt("edge.attr.comb") #trasnform as undirected and collpsing edges weight
)

climate_change_adj <- as_adjacency_matrix(
  arxiv_climate_change_network,
  type = c("both"),
  attr = NULL,
  edges = FALSE,
  names = TRUE,
  sparse = igraph_opt("sparsematrices")
)

length(V(arxiv_climate_change_network))
length(E(arxiv_climate_change_network))
cluster_fast_greedy(arxiv_climate_change_network, weights = E(arxiv_climate_change_network)$weight)
```


Subset network: largest giant connected component (lgcc)
```{r}
#largest giant connected component 
components <- igraph::clusters(arxiv_climate_change_network, mode="weak")
biggest_cluster_id <- which.max(components$csize)

# ids
vert_ids <- V(arxiv_climate_change_network)[components$membership == biggest_cluster_id]

# subgraph
arxiv_climate_change_network_sub <- igraph::induced_subgraph(arxiv_climate_change_network, vert_ids)
length(V(arxiv_climate_change_network_sub))
length(E(arxiv_climate_change_network_sub))

##Community structure detection based fast greedy
fc_climate_change_sub <- cluster_fast_greedy(arxiv_climate_change_network_sub, weights = E(arxiv_climate_change_network_sub)$weight)
fc_climate_change_sub
```

Plot phylogram on lgcc
```{r}
par(bg = 'black') # set background to black
plot_dendrogram(fc_climate_change_sub, mode="phylo", colbar = palette(), cex=0.8)
```

Plot network: lgcc
```{r}
#node degree based on its total degree
V(arxiv_climate_change_network_sub)$degree <- strength(graph = arxiv_climate_change_network_sub, mode="all")

#png("net_climate_change_sub.png", width=600, height=350, res=300)
#pdf(file = "climate_change_0712_net.pdf"   # The directory you want to save the file in
    #) # The height of the plot in inches
par(bg = 'black') # set background to black
plot(arxiv_climate_change_network_sub, 
  vertex.color =  membership(fc_climate_change_sub), 
  #vertex.size = 0,
  vertex.size = V(arxiv_climate_change_network_sub)$degree/300,
  vertex.label.color = membership(fc_climate_change_sub), 
  #vertex.label.cex = log(V(arxiv_climate_change_network_sub)$degree)/100, #vertex label size
  vertex.label.cex = V(arxiv_climate_change_network_sub)$degree/150, #vertex label size
  vertex.label.dist = 0,
  edge.color = 'white', 
  edge.width = E(arxiv_climate_change_network_sub)$weight/60,   
  main = 'Bigram Network: Climate Change', 
  alpha = 100, edge.curved=0.4
)
#dev.off()
```


Plot 3D network: lgcc
```{r}
#3D visualization
sj_list <- igraph_to_networkD3(arxiv_climate_change_network, what = "both", group=membership(fc_climate_change))

arxiv_climate_change_network_10 <- forceNetwork(Links = sj_list$links, Nodes = sj_list$nodes, Source = 'source',
             Target = 'target', NodeID = 'name', Group = 'group', linkWidth=sj_list$links$value/10,
             zoom = TRUE, linkDistance = 5)
	
saveNetwork(arxiv_climate_change_network_10, 'arxiv_climate_change_network_10.html', selfcontained = TRUE)
```

